On the probability of finding nonphysical solutions through shadowing\tnoteref{1}

### 2021-04-23 main_els.tex
Add summary of revisions.

In view of the plucked tent map, we can further question the
validity of numerical solutions. Can numerical solutions play 
the role of the plucking perturbation to the 
governing equation? That is, can numerical solutions represent 
slight perturbations to the governing equations for which the physical 
distribution is drastically different from the physical distribution 
of the original governing equation? Sauer \cite{sauer} has shown 
examples in which numerical error due to computation in double-precision floating point arithmetic causes significant change in the stationary probability distribution on the attractor. \reviewerOne{Some authors \cite{cns2}\cite{cns3} resort to Clean Numerical Simulations to tackle scenarios that demand highly accurate long-term prediction of chaotic orbits. When using double-precision arithmetic however, these works  \cite{cns}\cite{cns1}\cite{cns2}\cite{cns3} show that large errors result in statistical measures such as power spectra and spatio-temporal correlation functions.} The plucked tent map adds to this list of examples by demonstrating a mechanism to produce an extreme non-smooth response (Supplementary Material section \ref{sec:pluckedTentMap}).

>>>>

In view of the plucked tent map, we can further question the
validity of numerical solutions. Can numerical solutions play 
the role of the plucking perturbation to the 
governing equation? That is, can numerical solutions represent 
slight perturbations to the governing equations for which the physical 
distribution is drastically different from the physical distribution 
of the original governing equation? Sauer \cite{sauer} has shown 
examples in which numerical error due to computation in double-precision floating point arithmetic causes significant change in the stationary probability distribution on the attractor. \reviewerOne{Some authors} \cite{cns2}\cite{cns3} \reviewerOne{resort to Clean Numerical Simulations to tackle scenarios that demand highly accurate long-term prediction of chaotic orbits. When using double-precision arithmetic however, these works}\cite{cns}\cite{cns1}\cite{cns2}\cite{cns3}\reviewerOne{show that large errors result in statistical measures such as power spectra and spatio-temporal correlation functions.} The plucked tent map adds to this list of examples by demonstrating a mechanism to produce an extreme non-smooth response (Supplementary Material section \ref{sec:pluckedTentMap}).

\reviewerTwo{Here, we raise questions on the statistical consistency on numerical simulations of chaotic systems because they are traditionally interpreted as being shadowed by a true solution. }\reviewerTwo{Since shadowing solutions can be nonphysical, so can numerical solutions that lie close to them at all times, and hence have a long-term statistical distribution close to their shadowing counterparts.} \reviewerTwo{This argument holds even when numerical solutions are interpreted as perturbed solutions to the true dynamics that produce the same or a nearby attractor.}\reviewerTwo{The probability distribution on the attractor, measured by the amount of time a solution spends in each location on the attractor, can be drastically different for a numerical solution than a typical solution of the dynamics.}
